### 2016-05-09 ch03-lrm/truncation.tex
Truncation: labels uniform

\label{sec:nonparametric:truncation}
\researchBasedOn[This section]{Lumori2014TIM}
%FIXME: {labels into standardized form}

@@

\begin{assumption}\label{ass:imprespdecay}
The impulse response $g(t)$ decays exponentially over time, i.e. 
\[
  \exists A \in \PositiveRealNumbers, 
  \exists a > 0 ,
  \exists t_0 > 0,
  \forall t > t_0: 
     \abs{g(t)} \leq A \exp(- a t) \text{.}
\]
\end{assumption}

\begin{assumption}\label{ass:decay90perctime}
Within $90\%$ of the measurement window, the impulse response decays
 to a level that is indistinguishable from the noise.
\end{assumption}

Note that \assref{ass:imprespdecay} and \assref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.

@@

According to \assref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by \assref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the    average value of the impulse response. The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
To this end, the following procedure is executed:

@@

\begin{enumerate}
  \item The impulse response $\hat{g}_{\LPM}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. 
If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

@@

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \latin{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per \assref{ass:decay90perctime}.

@@

\subsection{Conclusion}
\label{sec:nparam:trunc:conclusion}

This section introduced a time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}. 
It consisted of, after obtaining the \gls{FRF} from the \gls{LPM}, computing the associated estimated impulse response via the \gls{IDFT}.
Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.

>>>>

\label{sec:nonparametric:truncation}
\researchBasedOn[This section]{Lumori2014TIM}

@@

\begin{assumption}\label{ass:trunc:impulseReponse:decay}
The impulse response $g(t)$ decays exponentially over time, i.e. 
\[
  \exists A \in \PositiveRealNumbers, 
  \exists a > 0 ,
  \exists t_0 > 0,
  \forall t > t_0: 
     \abs{g(t)} \leq A \exp(- a t) \text{.}
\]
\end{assumption}

\begin{assumption}\label{ass:trunc:impulseResponse:lastSegmentNoise}
Within $90\%$ of the measurement window, the impulse response decays to a level that is indistinguishable from the noise.
\end{assumption}

Note that \assref{ass:trunc:impulseReponse:decay} and \assref{ass:trunc:impulseResponse:lastSegmentNoise} exclude the possibility of considering a system that is a pure integrator.

@@

According to \assref{ass:trunc:impulseReponse:decay}, the true impulse response tends to zero asymptotically; and by \assref{ass:trunc:impulseResponse:lastSegmentNoise}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the    average value of the impulse response. The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
To this end, the following procedure is executed:

@@

\begin{enumerate}
  \item The impulse response $\hat{g}_{\LPM}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. 
If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By \assref{ass:trunc:impulseResponse:lastSegmentNoise}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

@@

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \latin{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per \assref{ass:trunc:impulseResponse:lastSegmentNoise}.

@@

\subsection{Conclusion}
\label{sec:nparam:trunc:conclusion}
This section introduced a time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}. 
It consisted of, after obtaining the \gls{FRF} from the \gls{LPM}, computing the associated estimated impulse response via the \gls{IDFT}.
Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
